Reply to reviewers\\ LMCS \#\,6784 Manuscript: \\``Compositional equivalences based on Open pNets''

### 2021-10-13 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
t_i to solve problem
letter: sentence on choice and weak bisim

\begin{quote}
Indeed, the plus operator of CCS does not verify the requirements ``non-observability of tau transitions'' for the weak bisimulation to be a congruence. We can define the weak bisimulation for CCS but it does not verify the congruence property. \TODO{define the bisimulation, or encode the nondeterministic choice operator ?}

This is now illustrated by Example 4 and 5 in the article.
\end{quote}

@@

P4 L20 A minor point: Technically, $a^{i\in 3}$ is not allowed by your syntax since indices need to also appear as a subscript.
\begin{quote}
\TODO{on a oublie celui-la... ?}
\end{quote}

>>>>

\begin{quote}
Indeed, the plus operator of CCS does not verify the requirements ``non-observability of tau transitions'' for the weak bisimulation to be a congruence. 
We can encode a choice operator for CCS and derive the weak bisimulation for processes with this operator, 
but this weak bisimulation does not verify the requirements for the congruence property. This is consistent with the fact that weak bisimulation is not a congruence for CCS, and our formalism allows us to explain why.

This is now explained and illustrated by Example 4 and 5 in the article.
\end{quote}

@@
